FictionEro - Data Cleaning

### 2024-06-06 analysis/1_cleaning.qmd
make analysis html not self contained so that we can easily access the figures

---
title: "FictionEro - Data Cleaning"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: true
    toc: true
---

@@

df <- read.csv("../data/rawdata_participants.csv") |> 
  mutate(across(everything(), ~ifelse(.x == "", NA, .x))) |>
  mutate(Sample = case_when(
    Language=="English" & str_detect(Experimenter, "reddit") ~ "Reddit",
    Language=="English" & Experimenter %in% c("2discord1", "Experimenter2", "Experimenter1") ~ "Student",
    Language=="English" & Experimenter %in% c("Unknown", "Readme (GitHub)", "website") ~ "Other",
    .default = Experimenter
  ))

@@

# Table
table_recruitment <- function(df) {
  summarize(df, N = n(), .by=c("Language", "Sample")) |> 
    arrange(desc(N)) |> 
    gt::gt() |> 
    gt::opt_stylize() |> 
    gt::opt_interactive(use_compact_mode = TRUE) |> 
    gt::tab_header("Number of participants per recruitment source")
}
table_recruitment(df)
```

@@

```{r}
# df <- filter(df, Mobile == "False")
dftask <- filter(dftask, Participant %in% df$Participant)
```

@@

df <- filter(df, Sex != "Other" & SexualOrientation != "Other")
dftask <- filter(dftask, Participant %in% df$Participant)
```

@@

@@

@@

@@

write.csv(df, "../data/data_participants.csv", row.names = FALSE)
write.csv(dftask, "../data/data.csv", row.names = FALSE)
```

>>>>

---
title: "FictionEro - Data Cleaning"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
---

@@

df <- read.csv("../data/rawdata_participants.csv") |> 
  mutate(across(everything(), ~ifelse(.x == "", NA, .x))) |>
  mutate(Sample = case_when(
    Language=="English" & Experimenter %in% c("2discord1", "Experimenter2", "Experimenter1") ~ "Students (Non-incentivized)",
    Language=="English" & Experimenter %in% c("Unknown", "Readme (GitHub)", "website", "reddit") ~ "General Population",
    Experimenter %in% c("enter", "macre", "piaca", "unime", "classroom1") ~ "Students (Non-incentivized)",
    Experimenter %in% c("SONA") ~ "Students (Incentivized)",
    Experimenter %in% c("gacon", "mafas", "marmar", "mavio", "sobon", "RISC", "Snowball") ~ "General Population",
    str_detect(Experimenter, "reddit") ~ "General Population",
    .default = Experimenter
  ))

@@

# Table
table_recruitment <- function(df) {
  summarize(df, N = n(), .by=c("Language", "Experimenter")) |> 
    arrange(desc(N)) |> 
    gt::gt() |> 
    gt::opt_stylize() |> 
    gt::opt_interactive(use_compact_mode = TRUE) |> 
    gt::tab_header("Number of participants per recruitment source")
}
table_recruitment(df)
```

@@

```{r}
# df <- filter(df, Mobile == "False")
# dftask <- filter(dftask, Participant %in% df$Participant)
```

@@

df <- filter(df, !(Sex == "Other" | SexualOrientation == "Other"))
dftask <- filter(dftask, Participant %in% df$Participant)
```

@@

```{r p_pornfactor}
#| fig-width: 14
#| fig-height: 14

dat <- select(df, COPS_Duration_1, COPS_Frequency_2, SexualActivity) |> 
    mutate(across(where(is.character), as.factor)) |> 
    mutate(across(where(is.factor), as.numeric))

r <- correlation::correlation(
  dat) |> 
  as.matrix()

r <- parameters::factor_analysis(dat, n = 1, rotation = "oblimin", cor = r)
df$Porn <- get_scores(r)[, 1]
```

@@

```{r}
n <- n_factors(select(df, starts_with("GAAIS")))
n
parameters::factor_analysis(
  select(df, starts_with("GAAIS")), 
  n=2, 
  rotation="oblimin")

df$GAAIS_Negative <- rowMeans(select(df, starts_with("GAAIS_Negative")))
df$GAAIS_Positive <- rowMeans(select(df, starts_with("GAAIS_Positive")))
```

@@

```{r}
glm(Feedback_AILessArousing ~ BAIT_Visual * AI_Knowledge, 
    data=mutate(df, Feedback_AILessArousing = ifelse(Feedback_AILessArousing=="True", 1, 0)), 
    family="binomial") |> 
  parameters::parameters() |> 
  display(title="Predicting 'AI was less arousing'")
```

```{r}
glm(Feedback_AIMoreArousing ~ BAIT_Visual * AI_Knowledge, 
    data=mutate(df, Feedback_AIMoreArousing = ifelse(Feedback_AIMoreArousing=="True", 1, 0)), 
    family="binomial") |> 
  parameters::parameters() |> 
  display(title="Predicting 'AI was more arousing'")
```

@@

setdiff(unique(df$Participant), unique(dftask$Participant))
write.csv(df, "../data/data_participants.csv", row.names = FALSE)
write.csv(dftask, "../data/data.csv", row.names = FALSE)
```
